RSM - Call for papers on data visualization

### 2020-03-19 README.Rmd
Add new paper to README

* Tanneru, Karthik, et al. "[Meta-analysis and systematic review of intermediate-term follow-up of prostatic urethral lift for benign prostatic hyperplasia.](https://link.springer.com/article/10.1007/s11255-020-02408-y)" International Urology and Nephrology (2020): 1-10.
* Veloso, Andreia, et al.. "[Effectiveness of Cognitive Training for School-Aged Children and Adolescents With Attention Deficit/Hyperactivity Disorder: A Systematic Review.](https://www.frontiersin.org/articles/10.3389/fpsyg.2019.02983/full)" Frontiers in Psychology 10 (2020): 2983.
* Simillis, Constantinos, et al. "[Postoperative chemotherapy improves survival in patients with resected high‐risk stage II colorectal cancer: results of a systematic review and meta‐analysis.](https://onlinelibrary.wiley.com/doi/pdf/10.1111/codi.14994)" Colorectal Disease (2020).
* Habadi, Mohammed Ibrahim, et al. "[Prevalence of Panic Disorders in the Primary Health Care Setting: A Systematic Review and Meta-Analysis.](https://www.ecronicon.com/ecmi/pdf/prevalence-of-panic-disorders-in-the-primary-health-care-setting-a-systematic-review-and-meta-analysis.pdf)" EC Microbiology 16.1 (2019): 01-09.
* Gibb, Kate, et al. "[The consistent burden in published estimates of delirium occurrence in medical inpatients over four decades: a systematic review and meta-analysis study.](https://www.medrxiv.org/content/medrxiv/early/2019/08/29/19005165.full.pdf)" medRxiv (2019): 19005165.

>>>>

* Perivoliotis, Konstantinos, et al. "[Comparing the efficacy and safety of laparoscopic and robotic adrenalectomy: a meta-analysis and trial sequential analysis.](https://link.springer.com/article/10.1007/s00423-020-01860-9)" Langenbeck's Archives of Surgery (2020): 1-11.
* Adile, Ashley A., et al. "[Salvage therapy for progressive, treatment-refractory or recurrent pediatric medulloblastoma: a systematic review protocol.](https://systematicreviewsjournal.biomedcentral.com/articles/10.1186/s13643-020-01307-8)" Systematic Reviews 9.1 (2020): 1-9.
* Tanneru, Karthik, et al. "[Meta-analysis and systematic review of intermediate-term follow-up of prostatic urethral lift for benign prostatic hyperplasia.](https://link.springer.com/article/10.1007/s11255-020-02408-y)" International Urology and Nephrology (2020): 1-10.
* Veloso, Andreia, et al.. "[Effectiveness of Cognitive Training for School-Aged Children and Adolescents With Attention Deficit/Hyperactivity Disorder: A Systematic Review.](https://www.frontiersin.org/articles/10.3389/fpsyg.2019.02983/full)" Frontiers in Psychology 10 (2020): 2983.
* Simillis, Constantinos, et al. "[Postoperative chemotherapy improves survival in patients with resected high‐risk stage II colorectal cancer: results of a systematic review and meta‐analysis.](https://onlinelibrary.wiley.com/doi/pdf/10.1111/codi.14994)" Colorectal Disease (2020).
* Habadi, Mohammed Ibrahim, et al. "[Prevalence of Panic Disorders in the Primary Health Care Setting: A Systematic Review and Meta-Analysis.](https://www.ecronicon.com/ecmi/pdf/prevalence-of-panic-disorders-in-the-primary-health-care-setting-a-systematic-review-and-meta-analysis.pdf)" EC Microbiology 16.1 (2019): 01-09.
* Gibb, Kate, et al. "[The consistent burden in published estimates of delirium occurrence in medical inpatients over four decades: a systematic review and meta-analysis study.](https://www.medrxiv.org/content/medrxiv/early/2019/08/29/19005165.full.pdf)" medRxiv (2019): 19005165.

### 2020-03-19 RSM-paper/manuscript.Rmd

ggplot2::ggsave(
          filename = "figs/Fig1-rob-traffic-light-plot.tiff",
          plot = tfplot,
          width = 7,
          height = 8,
          dpi = 1500
          )

@@

ggplot2::ggsave(
          filename = "figs/Fig2-rob-summary-barplot.tiff",
          plot = sumplot,
          width = 8,
          height = 2.41,
          dpi = 1500
          )

>>>>

ggplot2::ggsave(
          filename = "figs/Fig1-rob-traffic-light-plot.tiff",
          plot = tfplot,
          width = 7,
          height = 8,
          dpi = 600
          )

@@

ggplot2::ggsave(
          filename = "figs/Fig2-rob-summary-barplot.tiff",
          plot = sumplot,
          width = 8,
          height = 2.41,
          dpi = 600
          )
